### 2019-06-25 papers/journal/bio.tex
Minor Update
Introduction is added with the Synthesis as a Part

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
%The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%%
%In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%%
%These predictions are intended to be used as guides for future experiments. 
%%
%A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%%
%Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a set of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
%
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
\subsection{Combinatorial problem and use of Formal methods}
\noindent The analysis of VTS is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered for the same reason.

In previous work, a sampling approach was undertaken. 
%
The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached. 
%
With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
%
Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
%
It is possible that a different scheme for the dynamics could lead to a different set of solutions.

%Previous analyses of vesicle traffic networks dealt with this combinatorial
%explosion by using a sampling approach~\cite{mani2016stacking}. 
%
%In these analyses, vesicle traffic is modelled as an update system. 
%
%The traffic rule specifies how the system transitions from one
%time point to the next. 
%
%Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
%
%The update rule defines the flux transition for the next step. 
%
%This process is performed until a steady state is reached. 
%
%
%By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
%

In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
%
We would also like to directly make statements about steady state properties, rather
than using transition dynamics to the first search for steady states. 
%
Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
%
The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
%

@@

% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 

@@

% Note that the formulas define among other things constraints over
% paths between nodes in the graph model of VTS. Similarly, one can
% define fusion rules as constraints over the boolean functions modeling
% the regulations.  
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
%\begin{itemize}
%\item \srivas{Detailed BIO to Graph problem}
%\end{itemize}
%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e. the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.  Here we have defined the property by checking over existence of any fusion/budding rules.  We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
%\subsection{Converting the Graph Problem into Boolean SAT problem}
%\label{subsec:satproblem}
%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.  In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.  We then used the CBMC model checker to convert the graph problem into a SAT problem.  One of the challenges we had in our earlier work is dealing with quantifiers.  Note that the connectedness property defined in Listing~1.2 has quantifier alternation.  Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.   CBMC supports only a quantifier-free logic n its assertion language.  In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.  This enumeration was one source of bottleneck for scaling in our earlier work.  In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.  The details of te hnew encding will described in subsequent sections.
%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
%This property of VTSs has been considered informative and studied by~\cite{shukla}.
%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
\subsection{Synthesis of VTS }
\noindent The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}. 
Completing the VTS is a difficult task for many important reasons: 
\begin{enumerate}
    \item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
    \item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
    \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
    \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
    \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}

Nonetheless, completing the VTS for different organisms is very useful. 
%
Many diseases are caused by the malfunction of the VTS. 
%
Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network. 
%
This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%
\input{fig3}
\begin{example}
    In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Fig.~\ref{fig:synth-vts2} present it's complete output VTS. Every molecule present on the node is active. The activity of the molecules on an edge is determined by the presence of the other molecules. Each label represent particular type of molecule. The synthesis is performed against the stability and 3-connectivity. Synthesized edge is in red color and synthesized molecules are presented in blue. The synthesis adds one edge and 7 molecules to complete the partial VTS. For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
\end{example}
%
We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

%
The rest of the paper is organized as follows. 
%
In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
%
In Section~\ref{sec:model}, we present a formal model of VTSs and in Section~\ref{sec:property} the properties of interest.
%
In Section~\ref{sec:problem}, we present the formal problem statements of different search problems of VTS.
%
In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
%
In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
%
In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~

>>>>

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
%The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%%
%In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%%
%These predictions are intended to be used as guides for future experiments. 
%%
%A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%%
%Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a set of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
\input{fig3}
\begin{example}
	In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Fig.~\ref{fig:synth-vts2} present it's complete output VTS. Every molecule present on the node is active. The activity of the molecules on an edge is determined by the presence of the other molecules. Each label represent particular type of molecule. The synthesis is performed against the stability and 3-connectivity. Synthesized edge is in red color and synthesized molecules are presented in blue. The synthesis adds one edge and 7 molecules to complete the partial VTS. For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes. 
	%The presented graph is a subgraph of a VTS discussed in details in appendix.
\end{example}

%
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
%\subsection{Combinatorial problem and use of Formal methods}
%\noindent 
%The analysis of VTS is a difficult problem
%because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool

@@

% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
%
%
% Note that the formulas define among other things constraints over
% paths between nodes in the graph model of VTS. Similarly, one can
% define fusion rules as constraints over the boolean functions modeling
% the regulations.  
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
%\begin{itemize}
%\item \srivas{Detailed BIO to Graph problem}
%\end{itemize}
%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e. the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.  Here we have defined the property by checking over existence of any fusion/budding rules.  We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
%
%\subsection{Converting the Graph Problem into Boolean SAT problem}
%\label{subsec:satproblem}
%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.  In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.  We then used the CBMC model checker to convert the graph problem into a SAT problem.  One of the challenges we had in our earlier work is dealing with quantifiers.  Note that the connectedness property defined in Listing~1.2 has quantifier alternation.  Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.   CBMC supports only a quantifier-free logic n its assertion language.  In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.  This enumeration was one source of bottleneck for scaling in our earlier work.  In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.  The details of te hnew encding will described in subsequent sections.
%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
%
%This property of VTSs has been considered informative and studied by~\cite{shukla}.
%
%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
%\subsection{Synthesis of VTS }

@@

%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~

### 2019-06-25 papers/journal/intro.tex
Introduction is added with the Synthesis as a Part

\noindent A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
%
These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~

>>>>

\noindent 
%A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
The cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the
nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
%These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
%%The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
%%Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
%%Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
%%However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
%%In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
%
Cargo is moved between these organelles in small membrane-bound
transporters known as vesicles \cite{stenmark2009rab}.
%s

This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
%
Membrane traffic underpins nearly every aspect of eukaryotic cellular
physiology, including human cellular physiology.
%
Defects in membrane traffic lead to a variety of disorders or even
cell death \cite{stenmark2009rab}.
%
Understanding how membrane traffic functions is therefore one of the
central challenges of cell biology.
%
Some progress has been made, as cell biologists have assembled a
“parts list” of molecules that drive vesicle
traffic~\cite{dacks2007evolution}.
%
The essential processes involve the creation of vesicles loaded with
cargo from source organelles, known as “budding”, and the depositing
of those vesicles and cargo into target organelles, known as “fusion”
\cite{munro2004organelle}.
%
Budding is regulated by proteins known as coats and adaptors that
select cargo.
%
Fusion is regulated by proteins known as SNAREs and tethers, that
ensure that vesicles fuse to the correct target
\cite{mani2016stacking}.
%
Although we know a great deal about molecular-level details, there has
been very little work done on how such processes are integrated across
scales to build the entire vesicle traffic system (VTS).
%
We have recently attempted to use ideas of graph theory to address
this question \cite{mani2016stacking,shukla2017discovering}.

The SNARE proteins and the constraints that SNARE-to-SNARE regulations
impose on feasibile behaviors of VTSs are the focus of
our current work.
%
Abstractly, we can think of these proteins as labels that are
collected from the source compartment and taken to the target
compartment on vesicles.
%
There is a corresponding set of label molecules on the target compartments.
%
If the two sets of labels (on vesicles and targets) are compatible,
then the vesicle will fuse.
%
The question is: does this physical picture place any constrains on
the global topology of the traffic graph? We have previously shown that one informative constraint is graph connectivity \cite{shukla2017discovering}.
%
The intricacies of SNARE regulation are largely unknown.
%
How stringent SNARE regulation is can determine whether graph
topologies of particular level of connectivity are biologically
realizable.
%
For example, if SNAREs are completely unregulated and thus always
active, they cannot be used to generate a traffic network.
%
If these SNAREs are regulated by relatively simple rules then only
highly connected traffic networks can be generated using them.
%
The question is can we work toward a predictive analytical framework
of VTSs?

Another interesting question is the completion of the VTS. 
%
The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the VTS is a difficult task for many important reasons: 
\begin{enumerate}
	\item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
	\item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
	\item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}

Nonetheless, completing the VTS for different organisms is very useful. 
%
Many diseases are caused by the malfunction of the VTS. 
%
Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network. 
%
This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%

The analysis of VTSs is a difficult problem because
of the combinatorial scaling of possible traffic topologies and
regulatory rules.
%
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered for the same reason.

In previous work, a sampling approach was undertaken. 
%
The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached. 
%
With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
%
Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
%
It is possible that a different scheme for the dynamics could lead to a different set of solutions.

%Previous analyses of vesicle traffic networks dealt with this combinatorial
%explosion by using a sampling approach~\cite{mani2016stacking}. 
%
%In these analyses, vesicle traffic is modelled as an update system. 
%
%The traffic rule specifies how the system transitions from one
%time point to the next. 
%
%Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
%
%The update rule defines the flux transition for the next step. 
%
%This process is performed until a steady state is reached. 
%
%
%By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
%

In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
%
We would also like to directly make statements about steady state properties, rather
than using transition dynamics to the first search for steady states. 
%
Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
%
Formal verification tools, such as model checkers
\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
	cimatti2000nusmv, holzmann1997model} and SAT solvers
\cite{moskewicz2001chaff,een2004extensible} serve precisely this
purpose.
%
The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
%

%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
\subsection{Previous work and our Contribution}
In a recent work, we employed the model checker CBMC \cite{CKY03,
	ckl2004} meant to analyze ANSI C programs for studying this problem.
%
In this work, VTSs and SNARE regulations were modeled as C code mostly
using arrays to represent graphs and boolean tables.
%
Queries about graph connectivity requirements for different variations
of SNARE Regulations were modeled as logical assertions to be checked
by the model checker.
%
CBMC uses its own built-in encodings to reduce the analysis problem to
boolean satisfiability problem which is solved using SAT solvers.
%
This work was successful in demonstrating the feasibility of this
technology to this domain.
%
However, the scalability of this approach was limited (up to VTSs
with 7-8 nodes) due to the following reasons:
\begin{enumerate}
	\item The encoding used to model VTSs was not completely fine-tuned
	to the structure of the problem.
	\item The queries to be solved involve quantified formulas, i.e., we
	needed to solve queries of the form ``\emph{for all} graphs does there
	\emph{exist} SNARE regulation constraints that satisfy biological
	steady state.
\end{enumerate} As CBMC does not directly support solving such
quantified formulas, we had to use a technique that combined
non-determinism and partial enumeration that is not as
efficient.\newline

%
In this paper, we have developed a novel SAT encoding for
searching a VTS that satisfy the given properties.
%
We improved the encoding of some of the conditions for VTSs.
%
In the earlier implementation, reachability was encoded by
enumeration of paths.
%
In our encoding, we have recursively defined the reachability condition
such that that we avoid the exponential enumeration.
%
We have also encoded $k$-connectivity in the similar fashion and
avoided a blowup in the formula size.
%

We have implemented the encoding using Z3~\cite{z3} python API and searched for
VTS satisfying various properties upto size 14-18 nodes as compare
earlier tool that could only search graph upto size 7-8 nodes.
%
Since most VTSs in the cells are of 10 compartments,
our tool will be useful for biologists to study VTSs.
%
Furthermore, our encoding supports several variations of
the conditions.\newline

The following are the contributions of this work:
\begin{itemize}
	\item We have added novel encoding reachability and 3-4 connectivity
	\item Direct encoding into the SAT solver
	\item A user friendly and scalable tool based on well known SMT solver Z3
\end{itemize}

\par We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

%
The rest of the paper is organized as follows. 
%
In Section~\ref{sec:bio}, we present the biological background and details to understand the VTS. 
%
In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
%
In Section~\ref{sec:model}, we present a formal model of VTSs and in Section~\ref{sec:property} the properties of interest.
%
In Section~\ref{sec:problem}, we present the formal problem statements of different search problems of VTS.
%
In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
%
In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
%
In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~
